Measurement of ($\pi^-$-Ar) and ($K^+$-Ar) total hadronic cross sections at the LArIAT experiment

### 2018-05-31 AppendixC-EnergyCalibration/C-EnergyCalibration.tex
s

\textcolor{red}{Add agreement between data and MC for dedx for pions}

@@

\begin{figure}[htb]
\centering
\includegraphics[width=0.50\textwidth]{Chapter-5/Images/RunIINegTotaldEdXvsMomentum.png}
\includegraphics[width=0.50\textwidth]{Chapter-5/Images/RunIIPosTotaldEdXvsMomentum.png}
\caption{Stopping power versus Momentum for Run-II negative (top) and positive (bottom) polarity data. We achieve the agreement between the Bethe-Bloch predictions and the distribution obtained with of the positive pions (top plot, red dots) by tuning the calorimetry constants. Once the calorimetry constants are locked in, the agreement between the other particle species and the Bethe-Bloch predictions follows naturally.}
\label{fig:BBandData}
\end{figure}

>>>>

After the calibration is done separately on data and MC, we can compare the resulting dE/dX distributions; this is done for the set of pion beamline candidates and pion MC on the left side of Figure \ref{fig:dedx}. On the right side of the same figure, we report the data-MC comparison for the kaon sample used in the cross section. The distributions are fitted with simple Landau functions. As expected, the Landau MPV for data  is consistent with the MC MPV for both pions and kaons. For both the pion and the kaon case, the width of the Landau is a bit wider in data than in MC; this difference might be due to an underestimate of the electronic noise in the MC simulation.

@@

\begin{figure}[htb]
\centering
\includegraphics[width=0.48\textwidth]{Chapter-5/Images/RunIINegTotaldEdXvsMomentum.png}
\includegraphics[width=0.48\textwidth]{Chapter-5/Images/RunIIPosTotaldEdXvsMomentum.png}
\caption{Stopping power versus Momentum for Run-II negative (top) and positive (bottom) polarity data. We achieve the agreement between the Bethe-Bloch predictions and the distribution obtained with of the positive pions (top plot, red dots) by tuning the calorimetry constants. Once the calorimetry constants are locked in, the agreement between the other particle species and the Bethe-Bloch predictions follows naturally.}
\label{fig:BBandData}
\end{figure}

\begin{figure}[htb]
\centering
\includegraphics[width=0.48\textwidth]{AppendixC-EnergyCalibration/dEdXPions.pdf}
\includegraphics[width=0.48\textwidth]{AppendixC-EnergyCalibration/dEdXKaons.pdf}
\caption{\emph{Left:} dE/dx distribution for $\pi^-/\mu^-/e^-$ data (black) and Pion MC (blue). The Landau fit for data is shown in red, the one for MC in teal.\emph{Right:} dE/dx distribution for $K^+$ data (black) and Kaon MC (blue). The Landau fit for data is shown in red, the one for MC in teal. All the distributions are area normalized.}
\label{fig:dedx}
\end{figure}

### 2018-05-31 Chapter-3/3-TheLArIATExperiment.tex
s

The three wire planes and the cathode form three drift volumes, as shown in Figure \ref{fig:driftregions}. 
The main drift volume is defined as the region between the cathode plane and the shield plane (C-S). The other two drift regions are those between the shield plane and the induction plane (S-I), and between the induction plane and the collection plane (I-C). The electric field in these regions is chosen to satisfy the charge transparency condition and allow for 100$\%$ transmission of the drifting electrons through the shield and the induction planes.

\begin{figure}[htb]
\centering
\includegraphics[scale=0.35]{Chapter-3/Images/DriftRegions.png}\\
\caption{Schematic of the three drift regions inside the LArIAT TPC: the main drift volume between the cathode and the shield plane (C-S) in green, the region between the shield plane and the induction plane (S-I) in purple, and the region between the induction plane and the collection plane (I-C) in pink.}
\label{fig:driftregions}
\end{figure}

>>>>

The three wire planes and the cathode form three drift volumes, as shown in Figure \ref{fig:driftregions}. 
The main drift volume is defined as the region between the cathode plane and the shield plane (C-S). The other two drift regions are those between the shield plane and the induction plane (S-I), and between the induction plane and the collection plane (I-C). The electric field in these regions is chosen to satisfy the charge transparency condition  and allow for 100$\%$ transmission of the drifting electrons through the shield and the induction planes; for example, the transparency condition between for the shield plane reads
\begin{equation}
\frac{E_{S-I}}{E_{C-S}} > \frac{1+\rho}{1-\rho},
\end{equation}
where $E_{C-S}$ is the electric field in the region between the cathode and the shield plane, $E_{S-I}$ is the electric field in the region between the shield and the induction plane, and $\rho = \frac{2\pi \text{ }r}{D}$ is a factor accounting for the radius of the wires $r$ (152 $\mu m$) and the gap distance $D$ (4 mm). An analogous condition can be written for the induction plane.
\begin{figure}[htb]
\centering
\includegraphics[scale=0.35]{Chapter-3/Images/DriftRegions.png}\\
\caption{Schematic of the three drift regions inside the LArIAT TPC: the main drift volume between the cathode and the shield plane (C-S) in green, the region between the shield plane and the induction plane (S-I) in purple, and the region between the induction plane and the collection plane (I-C) in pink.}
\label{fig:driftregions}
\end{figure}
